Hydra Battles and Cie

### 2021-09-18 doc/part-hydras.tex
small changes

\begin{itemize}
\item Semi automatic tactics for proving inequalities $\alpha < \beta$, even when $\alpha$ and $\beta$ are not closed terms.
\item Extension to $\Gamma_0$ (in Veblen normal form)
\item More lemmas about hierarchies of rapidly growing functions, and their relationship 
    with primitive recursive functions and provability in Peano arithmetic 
(following~\cite{KS81, KP82}).
\item From \coq's point of view, this development could be used as an illustration of the evolution of the software, every time new libraries and sets of tactics could help to simplify the proofs.
\end{itemize}

>>>>

\begin{itemize}
\item Semi automatic tactics for proving inequalities $\alpha < \beta$, even when $\alpha$ and $\beta$ are not closed terms.
\item Extension to $\Gamma_0$ (in Veblen normal form)
\item More lemmas about hierarchies of rapidly growing functioit ns, and their relationship 
    with primitive recursive functions and provability in Peano arithmetic 
(following~\cite{KS81, KP82}).
\item From \coq's point of view, this development could be used as an illustration of the evolution of the software, every time new libraries and sets of tactics could help to simplify the proofs.
\end{itemize}
